---
title: "C67-Final Project"
author: "Eddie Shin"
date: "01/04/2022"
output: html_document
---

# Cover Page

```{r, message=FALSE}
library(tidyverse)
library(readxl)
```

```{r}
bike <- read_excel("SeoulBikeData.xlsx", skip=1, 
                   col_names=c("Date", "BikeCount", "Hour", "Temp", "Humid", "WindSpeed", "Visibility", "DewPointTemp", "SolarRad", "Rainfall", "Snowfall", "Season", "Holiday", "FuncDay"))
bike
```

# Background and Significance


# Model Selection

Which terms should we include in the model? main-effects, interactions or polynomial terms

## Main-Effects only Full Model

```{r}
# library(MASS)
fit.full <- lm(BikeCount ~ Temp + Humid + WindSpeed + Visibility + DewPointTemp + SolarRad + Rainfall + Snowfall + factor(Season) + factor(Holiday) + factor(FuncDay), data=bike)
summary(fit.full)
# step <- stepAIC(fit_full, direction="both")
```

Based on the summary of main-effect full model, we have the p-value of F-statistics < 2.2e-16 which is significant. The interpretation of a small p-value less than our $\alpha$ for F-statistic is that there is at least one of the predictor variables which is significant to the response variable.

We can see that most of the predictor variables look significant as they have small p-values. However, based on t-tests, `Visibility` and `DewPointTemp` have large p-values of 0.159 and 0.123 respectively. 

```{r}
fit.reduced.1 <- lm(BikeCount ~ Temp + Humid + WindSpeed + SolarRad + Rainfall + Snowfall + factor(Season) + factor(Holiday) + factor(FuncDay), data=bike)
summary(fit.reduced.1)
```

The first reduced model removed `Visibility` and `DewPointTemp` and it can be seen that $R^2 = 0.478$ and $R_{adj}^2 = 0.4774$ which remain unchanged from the full model. 


```{r}
library(MASS)
stepAIC(fit.reduced.1, direction="both")
```

Based on the result of stepAIC process, we have no change needed for the reduced model we obtained above. However, our $R^2$ is not high enough to make a conclusion. Are there any other ways to improve $R^2$ measure further?




```{r}
fit.main.effect <- lm(BikeCount ~ Temp + Humid + WindSpeed + Visibility + DewPointTemp + SolarRad + Rainfall + Snowfall + Season + Holiday + FuncDay, data=bike)
summary(fit.main.effect)
```

```{r}
library(leaps)
allreg <- regsubsets(BikeCount ~ Temp + Humid + WindSpeed + Visibility + DewPointTemp + SolarRad + Rainfall + Snowfall + Season + Holiday + FuncDay, data=bike, nbest=10)
n = dim(bike)[1]
aprout <- summary(allreg)
pprime <- apply(aprout$which, 1, sum)
aprout$aic <- aprout$bic - log(n) * pprime + 2 * pprime
with(aprout, round(cbind(which,rsq,adjr2,cp,bic,aic),3))
```

test
aLPHA