---
title: "C67-Final Project"
author: "Du Han"
output: html_document
---

# Cover Page

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(leaps)
library(MASS)
library(lmtest)
```

```{r}
bike <- read_excel("SeoulBikeData.xlsx", skip=1, 
                   col_names=c("Date", "BikeCount", "Hour", "Temp", "Humid", "WindSpeed", "Visibility", "DewPointTemp", "SolarRad", "Rainfall", "Snowfall", "Season", "Holiday", "FuncDay"))
bike
```
Plots the relationship of every explanatory variables to response variable
```{r}
bike %>%
pivot_longer(
-c(Date,BikeCount,Season,Holiday,FuncDay),
names_to="xname", values_to="Explanatory_Variables"
) %>%
ggplot(aes(x = Explanatory_Variables, y = BikeCount)) + geom_point() +
facet_wrap(~xname, scales = "free")

bike %>% ggplot(aes(x = BikeCount)) + geom_histogram(bins = 10)
```


```{r}
#Full model
fit.full <- lm(BikeCount+1 ~ Temp + Humid + WindSpeed + Visibility + DewPointTemp + SolarRad + Rainfall + Snowfall + factor(Season) + factor(Holiday) + factor(FuncDay), data=bike)
summary(fit.full)
result = boxcox(fit.full)
mylambda = result$x[which.max(result$y)]
```


Transform the response variable:



```{r}
#IHS transformation
Count_m.1 = log(bike$BikeCount+((bike$BikeCount^2+1)^0.5))
fit.1 <- lm(Count_m.1 ~ Temp + Humid + WindSpeed + Visibility + DewPointTemp + SolarRad + Rainfall + Snowfall + factor(Season) + factor(Holiday) + factor(FuncDay), data=bike)
summary(fit.1)
```

---------------------------------------------------------


```{r}
#box-cox transformation with lambda_1 = 0 and lambda_2 = 1
Count_m.2 = log(bike$BikeCount+1)
fit.2 <- lm(Count_m.2 ~ Temp + Humid + WindSpeed + Visibility + DewPointTemp + SolarRad + Rainfall + Snowfall + factor(Season) + factor(Holiday) + factor(FuncDay), data=bike)
summary(fit.2)
anova(fit.2)
```

Try to run AIC step for fit.2(1 shift)
```{r}

stepAIC(fit.2, direction="both")
```
This model has better AIC and same R^2 adj
```{r}
summary(lm(formula = Count_m.2 ~ Humid + WindSpeed + Visibility + DewPointTemp + 
    SolarRad + Rainfall + factor(Season) + factor(Holiday) + 
    factor(FuncDay), data = bike))
anova(lm(formula = Count_m.2 ~ Humid + WindSpeed + Visibility + DewPointTemp + 
    SolarRad + Rainfall + factor(Season) + factor(Holiday) + 
    factor(FuncDay), data = bike))
5165.6/(5164.8/8746)+2*12-8760
```
Cp is close to p' = 12

Try to add some interaction variables.
```{r}
fit.2.m <- lm(Count_m.2 ~ Humid + WindSpeed + Visibility + DewPointTemp + 
    SolarRad + Rainfall + factor(Season) + factor(Holiday) + factor(FuncDay) + Humid:Visibility + Humid:DewPointTemp +  SolarRad:Humid + Rainfall:Humid, data=bike)
summary(fit.2.m)
anova(fit.2.m)
extractAIC(fit.2.m)[2]
```
R^2 is a little bit higher, and small aic.


```{r}
ggplot(fit.2.m, aes(y = .resid, x = .fitted)) + geom_point()
ggplot(fit.2.m, aes(sample = .resid)) + stat_qq() + stat_qq_line()
```

---------------------------------------------------------

```{r}
#box-cox transformation with lambda_1 = 0 and lambda_2 = the square of the first quartile divided by the third quartile
Count_m.4 = log(bike$BikeCount+(quantile(bike$BikeCount,0.25)/quantile(bike$BikeCount,0.75))^2)
fit.4 <- lm(Count_m.4 ~ Temp + Humid + WindSpeed + Visibility + DewPointTemp + SolarRad + Rainfall + Snowfall + factor(Season) + factor(Holiday) + factor(FuncDay), data=bike)
summary(fit.4)
```

Try to run AIC step for fit.4(quartile shift)
```{r}
stepAIC(fit.4, direction="both")
```

This model has better aic and same R^2 adj
```{r}
summary(lm(formula = Count_m.4 ~ Humid + WindSpeed + Visibility + DewPointTemp + 
    SolarRad + Rainfall + factor(Season) + factor(Holiday) + 
    factor(FuncDay), data = bike))
```

```{r}
fit.4.m = lm(formula = Count_m.4 ~ Humid + WindSpeed + Visibility + DewPointTemp + 
    SolarRad + Rainfall + factor(Season) + factor(Holiday) + 
    factor(FuncDay)+ Humid:Visibility + Humid:DewPointTemp +  SolarRad:Humid + Rainfall:Humid, data = bike)
summary(fit.4.m)
extractAIC(fit.4.m)[2]
```
Still a little higher R^2 and small aic

---------------------------------------------------------

```{r}
#sqrt transformation
Count_m.5 = sqrt(bike$BikeCount)
fit.5 <- lm(Count_m.5 ~ Temp + Humid + WindSpeed + Visibility + DewPointTemp + SolarRad + Rainfall + Snowfall + factor(Season) + factor(Holiday) + factor(FuncDay), data=bike)
summary(fit.5)
anova(fit.5)
```

Try to run AIC step for fit.5(sqrt tansform)
```{r}
stepAIC(fit.5, direction="both")
AIC(lm(formula = Count_m.5 ~ Temp + Humid + WindSpeed + Visibility + 
    DewPointTemp + SolarRad + Rainfall + Snowfall + factor(Season) + 
    factor(Holiday) + factor(FuncDay), data = bike))
```
Same Model with no change
and since it's same model so Cp is just p'

```{r}
ggplot(fit.5, aes(y = .resid, x = .fitted)) + geom_point()
ggplot(fit.5, aes(sample = .resid)) + stat_qq() + stat_qq_line()
bptest(fit.5)
```

Add some interactions for sqrt transformation.
```{r}
fit.5.m <- lm(Count_m.5 ~ Temp + Humid + WindSpeed + Visibility + DewPointTemp + SolarRad + Rainfall + Snowfall + factor(Season) + factor(Holiday) + factor(FuncDay) + Humid:Visibility + Humid:DewPointTemp + SolarRad:Temp + SolarRad:Humid + Rainfall:Humid, data=bike)
summary(fit.5.m)
extractAIC(fit.5.m)[2]
```
Better R^2 than model without interaction, but AIC is too high


-------------------

```{r}
#box-cox with calculated lambda
Count_m.6 = (bike$BikeCount)^mylambda 
ggplot(,aes(x = Count_m.6)) + geom_histogram(bins = 10)
fit.6 <- lm(Count_m.6 ~ Temp + Humid + WindSpeed + Visibility + DewPointTemp + SolarRad + Rainfall + Snowfall + factor(Season) + factor(Holiday) + factor(FuncDay), data=bike)
summary(fit.6)
anova(fit.6)
```

Try to run AIC step for fit.2(1 shift)
```{r}
stepAIC(fit.6, direction="both")
```
This model has better AIC and same R^2 adj
```{r}
summary(lm(formula = Count_m.6 ~ Humid + WindSpeed + Visibility + DewPointTemp + 
    SolarRad + Rainfall + factor(Season) + factor(Holiday) + 
    factor(FuncDay), data = bike))
anova(lm(formula = Count_m.6 ~ Humid + WindSpeed + Visibility + DewPointTemp + 
    SolarRad + Rainfall + factor(Season) + factor(Holiday) + 
    factor(FuncDay), data = bike))
```


Try to add some interaction variables.
```{r}
fit.6.m <- lm(formula = Count_m.6 ~ Humid + WindSpeed + Visibility + DewPointTemp + 
    SolarRad + Rainfall + factor(Season) + factor(Holiday) + 
    factor(FuncDay) + Humid:Visibility + Humid:DewPointTemp +  SolarRad:Humid + Rainfall:Humid, data=bike)
summary(fit.6.m)
anova(fit.6.m)
extractAIC(fit.6.m)[2]
```
R^2 is a little bit higher, and small aic.


```{r}
ggplot(fit.6.m, aes(y = .resid, x = .fitted)) + geom_point()
ggplot(fit.6.m, aes(sample = .resid)) + stat_qq() + stat_qq_line()
```



Note: The built-in functions for calculating aic in R are AIC() and extractAIC(), they use different formula. 
For stepAIC, R is using extractAIC() so I use it to compare. But I have no idea which one does regsubsets() use.
For AIC(), sqrt still has highest value. 
Maybe we should try to use formula given by professor for the report.


```{r}
pairs(bike[3:11])
```
```{r}
cor(bike[3:11])
```





